dispRity manual

### 2020-05-04 inst/gitbook/index.Rmd
updated manual

--- 
title: "dispRity manual"
author: "Thomas Guillerme (guillert@tcd.ie), Mark Puttick (marknputtick@gmail.com) and  Natalie Cooper (natalie.cooper@nhm.ac.uk)"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [../References.bib, ../packages.bib]
link-citations: yes
github-repo: TGuillerme/dispRity
description: "dispRity R package vignette"
---

>>>>

--- 
title: "dispRity manual"
author: "Thomas Guillerme (guillert@tcd.ie),\nMark Puttick (marknputtick@gmail.com) and\nNatalie Cooper (natalie.cooper@nhm.ac.uk)"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [../References.bib, ../packages.bib]
link-citations: yes
github-repo: TGuillerme/dispRity
description: "dispRity R package vignette"
---
